\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{xcolor}

\geometry{
    a4paper,
    total={170mm,257mm},
    left=20mm,
    top=20mm,
}

\pagestyle{fancy}
\fancyhf{}
\rhead{MediMatch AI+ Evaluation}
\lhead{Team Contribution Report}
\cfoot{\thepage}

\title{\textbf{MediMatch AI+: Team Contribution \& Progress Report}}
\author{\textbf{Team MediMatch}}
\date{\today}

\begin{document}

\maketitle

\section{Project Status}
The \textbf{MediMatch AI+} Phase II implementation is \textbf{100\% Complete}. All targeted features (RAG Chatbot, Drug Comparison, Personal Library, Prescription OCR) have been deployed and verified.

\section{Individual Contributions}

% =========================================================================================
% VIGNYATHA - FRONTEND & UI/UX
% =========================================================================================
\subsection*{1. Y. Vignyatha Reddy (AM.EN.U4CSE22174)}
\textbf{Role:} \textit{Frontend \& UI/UX Lead}

\subsubsection*{Code Contribution}
\begin{itemize}
    \item \textbf{Web Interface Architecture}: Designed and implemented the complete suite of Jinja2/HTML templates (`index.html`, `target_prediction.html`, `visualize_kg.html`). Established the Global Design System based on \textbf{Glassmorphism} for a consistent user experience.
    \item \textbf{Interactive Components}: Developed modular JavaScript logic for dynamic updates (Modals, Dropdowns) and implemented client-side validation to ensure responsive feedback.
    \item \textbf{Data Visualization}: Integrated \textbf{Chart.js} to render the interactive Radar Charts for the Drug Comparison module and styled the Knowledge Graph container for optimal readability.
\end{itemize}

\subsubsection*{Mapping to Design}
\begin{itemize}
    \item \textbf{Visual Cohesion}: Fulfilled the requirement for a modern, accessible interface by creating a unified design language that works seamlessly across tablet and desktop views.
\end{itemize}

\hrulefill

% =========================================================================================
% CHARAN - OCR & MOBILE (NO RAG)
% =========================================================================================
\subsection*{2. M. Venkata Charan (AM.EN.U4CSE22333)}
\textbf{Role:} \textit{OCR Specialist \& Mobile Integration}

\subsubsection*{Code Contribution}
\begin{itemize}
    \item \textbf{Intelligent OCR Pipeline}: Integrated \textbf{Google Gemini Vision} to digitize handwritten prescriptions, implementing image pre-processing optimizations to maximize recognition accuracy.
    \item \textbf{Mobile Connectivity}: Configured the Flask backend to support key-based Authentication and \textbf{CORS} policies, enabling the Flutter mobile app to sync data.
    \item \textbf{Target Prediction Models}: Implemented the biological target prediction algorithms using molecular similarity logic (Tanimoto coefficients).
\end{itemize}

\subsubsection*{Mapping to Design}
\begin{itemize}
    \item \textbf{Smart Systems}: Bridged the gap between physical paper inputs (OCR) and digital records, fulfilling the "Digitization" pillar of the proposal.
\end{itemize}

\hrulefill

% =========================================================================================
% ANUDEEP - BACKEND & SECURITY
% =========================================================================================
\subsection*{3. B. Sai Anudeep (AM.EN.U4CSE22315)}
\textbf{Role:} \textit{Backend Architecture & Security Lead}

\subsubsection*{Code Contribution}
\begin{itemize}
    \item \textbf{Core Backend Development}: Architected the Flask application structure (`app.py`), blueprinting, and route management. Integrated the PDF Generation Service for prescription exports.
    \item \textbf{Database Management}: Designed the optimized SQLAlchemy ORM schema for `Users`, `Prescriptions`, and `Drugs`, managing all database migrations and efficient retrieval logic.
    \item \textbf{Security}: Implemented robust User Session Management, login/signup logic, and input sanitization to prevent injection attacks and ensure secure handling of medical data.
\end{itemize}

\subsubsection*{Mapping to Design}
\begin{itemize}
    \item \textbf{Robust Infrastructure}: Ensured the platform is scalable and secure, providing the foundational stability required for a medical application.
\end{itemize}

\hrulefill

% =========================================================================================
% PAVAN - RAG & DATA (RAG MOVED HERE)
% =========================================================================================
\subsection*{4. K. Pavan (AM.EN.U4CSE22330)}
\textbf{Role:} \textit{RAG Systems & Data Lead}

\subsubsection*{Code Contribution}
\begin{itemize}
    \item \textbf{RAG Pipeline}: Developed the entire Retrieval-Augmented Generation logic (`rag_engine.py`). Integrated \textbf{FAISS} for vector retrieval and \textbf{Groq (Llama 3)} for the AI Copilot.
    \item \textbf{Data Ecosystem}: Managed integrations with \textbf{ChEMBL} and \textbf{PubChem} APIs. Built the data cleaning and normalization pipelines for the "Drug Comparison" module.
    \item \textbf{Pharmacy Locator}: Implemented the \textbf{OpenStreetMap} integration and geolocation services to calculate distances and find nearby pharmacies.
\end{itemize}

\subsubsection*{Mapping to Design}
\begin{itemize}
    \item \textbf{Hybrid Intelligence}: Fulfilled the "AI Copilot" requirement by combining vector search with massive external datasets to provide hallucination-free medical answers.
\end{itemize}

\end{document}
